make STEAM clear

### 2019-12-15 mstemc/index.tex
use the org-macro to add the titlepage
which is handy to set the image in the front page. Also use the org macro I also
can set the copyright page.

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
                  \usetikzlibrary{arrows,decorations.pathmorphing}
                  \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Petri-Net In TiKZ Tutorial}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
 pdfkeywords={},
 pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\newcommand*{\titleCM}{\begingroup
\begin{center}
\vspace{\baselineskip}
{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
\vspace{2\baselineskip}   \newline
{\large Eason Zhang with www.makesteamclear.com \par}
\vspace{\baselineskip}          \newline
{\large \today \par}
\vspace{\baselineskip}
\vfill
\setlength{\unitlength}{3pt}
\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
\vfill
\vspace{\baselineskip}
{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
\vspace{\baselineskip}
{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way. If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
\end{center}
\endgroup}
\begin{titlepage}
\titleCM
\end{titlepage}
\tableofcontents

Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
me work through the code line by line. During this example, more tikz libraries
are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
\texttt{tikzpicture} environment.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
\end{center}
\end{document}

>>>>

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
       \usepackage{tikz}
       \usetikzlibrary{arrows,decorations.pathmorphing}
       \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Set up the TikZ in Emacs Org}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Set up the TikZ in Emacs Org},
 pdfkeywords={},
 pdfsubject={An introduction to setup the TikZ environment in Emacs Org File. So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par
 \end{center}
 \endgroup

 \newpage \textbf{copyright page} \newpage \tableofcontents \newpage

\hspace{0pt}\\

An introduction to setup the TikZ environment in Emacs Org File. So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.

\section{config the header args}
\label{sec:orga783c72}

You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
org-babel, you can generate ,insert and export the figure generated from Tikz
package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
introduction for beginners. Following it you may have a minimum working example
like below:

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400
#+header: :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
           shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\section{generate results with different formats}
\label{sec:org39c9b75}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\section{export the results according to the backend}
\label{sec:org58238bf}

You can set \texttt{:exports} to control how the results will be exported. Now I set it
as \texttt{none} which means the result will not be exported to latex or other format. I
want to set more options of the exports. So I use:

\begin{verbatim}
#+ATTR_HTML:  :width 800 :align center
#+ATTR_LATEX: :width 0.8\textwidth :align center
{{{if-latex(tutorial.pdf,tutorial.png)}}}
\end{verbatim}

\texttt{if-latex} is a Org MACRO whose definition is :
\begin{verbatim}
#+MACRO: if-latex (eval (if
(org-export-derived-backend-p org-export-current-backend 'latex)
 (concat "[[file:../../img/tikz/"  $1 "]]")
 (concat "[[file:../../img/tikz/"  $2 "]]") ))
\end{verbatim}

The \texttt{if-latex} MACRO let you export different formats by the backend. If the
backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
out without losing any resolution.

\section{the final workflow}
\label{sec:org0400fae}

The minimum working example at the start of this post is simplifed as below.

\begin{verbatim}
#+header: :file  "../../img/tikz/tutorial.pdf"
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src

#+RESULTS:
[[file:../../img/tikz/tutorial.png]]

The following is the generated figure.
#+ATTR_HTML:  :width 800 :align center
#+ATTR_LATEX: :width 0.8\textwidth :align center
{{{if-latex(tutorial.pdf,tutorial.png)}}}
\end{verbatim}

Many settings are grouped into a setup file which is included at the top of this
post:
\begin{verbatim}
#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
\end{verbatim}

Now, If you set the extension of the target file in the first line either \texttt{pdf} or
\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
org-toggle-inline-images}  , you can preview the result. If export the org-file
as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
export to other format, \texttt{png} image will be used.
\end{document}

### 2019-12-15 mstemc/mstemc.tex
use the org-macro to add the titlepage
which is handy to set the image in the front page. Also use the org macro I also
can set the copyright page.

% Intended LaTeX compiler: pdflatex
\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{make STEAM clear}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={make STEAM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\newcommand*{\titleCM}{\begingroup
\vspace*{\drop}
\begin{center}
\vspace{\baselineskip}
{\Huge \textbf{make STEAM clear} \par}
\vspace{2\baselineskip}   \newline
{\large Eason Zhang with www.makesteamclear.com \par}
\vspace{\baselineskip}          \newline
{\large \today \par}
\vspace{\baselineskip}
\vfill
\setlength{\unitlength}{3pt}
\makebox[\textwidth][c]{\includegraphics[width=0.2\textwidth]{\~/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
\vfill
\vspace{\baselineskip}
{\Large WWW.MAKESTEAMCLEAR.COM \par}\newline
\vspace{\baselineskip}
{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way. If you found the contents in this post or the site or the youtube channel helpful, please consider support me, thanks \par}
\end{center}
\vspace*{\drop}
\endgroup}
\begin{titlepage}
\titleCM
\end{titlepage}
\tableofcontents

\section{Videos}
\label{sec:orge61aa3c}

\section{Posts}
\label{sec:orgcd8829e}

\subsection{Set up the TikZ in Emacs Org}
\label{sec:org7c6689e}
\hspace{0pt}\\

@@

\subsubsection{config the header args}
\label{sec:org8a24a77}

@@

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\subsubsection{generate results with different formats}
\label{sec:org05b6333}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\subsubsection{export the results according to the backend}
\label{sec:orgff78033}

@@

\subsubsection{the final workflow}
\label{sec:orga6d2484}

@@

\subsection{Export Markdown and latex using Emacs Org}
\label{sec:orgd6fe22f}

@@

\subsubsection{Introduction}
\label{sec:orgd478c4d}

@@

\subsubsection{set up ox-hugo}
\label{sec:org76b6cf4}

@@

The first time you want to export an Org file or a subtree of an Org file, use
\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
\subsubsection{use Org Macro replacement}
\label{sec:orga32c0f1}

@@

Once you are familiar with Org Macro, It behaves beyond your imagination.
\subsubsection{use the setupfile for each Org file}
\label{sec:org589cab1}

@@

\subsection{Drawing Graphs Using TikZ in Emacs Org}
\label{sec:org220de70}

\subsubsection{Drawing a TikZ picture in Emacs Org Mode}
\label{sec:orgd491791}

\lstset{language=[LaTeX]TeX,label=a-minimum-working-example,caption={a minimum working example},captionpos=b,firstnumber=1,numbers=left}
\begin{lstlisting}
\usetikzlibrary{intersections,arrows.meta}
\begin{tikzpicture}[thin]
\draw (-1.5,0) -- (1.5,0);
\draw (0,-1.5) -- (0,1.5);
\filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
\draw (0,0) rectangle (.5,.5);
\draw (0,0) rectangle (-0.5,-0.5);
\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
% relative coordinate
\draw[blue, very thick] (30:1) ++ (0,-0.5) --(0,0);
% name a path without drawing it
\path[name path = upward line] (1,0) -- (1,1);
\path[name path = sloped line] (0,0) -- (30:1.5cm);
% use intersection of two path
\draw[name intersections={of = upward line and sloped line, by=x}]
     [very thick, orange] (1,0) -- (x);
% use arrow
\draw[<->>] (0,0) -- (145:1);
\draw[<-{Triangle[fill=red]}] (0,0) -- (30:1);
% use scope
\begin{scope}[very thick]
\draw (-0.4,0.4) -- (0.4,0.4);
\draw (-0.4,-0.4) -- (0.4,-0.4);
\end{scope}
% use foreach
\foreach \x in {-1cm,-0.5cm,1cm}
    \draw[red] (\x,-3pt) -- (\x,3pt);
\foreach \y in {-1cm,-0.5cm,1cm}
    \draw[red](-3pt,\y) -- (3pt,\y);
% using node
\draw (0,0)+(0.2,-0.2) node {\tiny $(0,0)$ };
\end{tikzpicture}
\end{lstlisting}

@@

\begin{enumerate}
\item In \hyperref[a-minimum-working-example]{the minimum working example} line 12 , a path is named  without drawing
it.
\item Line 16 gives an example of using library \texttt{intersections}. Note
that you need to add the library using \texttt{\textbackslash{}usetikzlibrary\{intersections\}}
otherwise an error occurs during \LaTeX compiling.
\item Line 18 and 19 gives an example of using arrow. To make it work,
\texttt{\textbackslash{}usetikzlibrary\{arrows.meta\}} is needed. The library \texttt{arrows.meta} provides tons
of types of arrows whick shock me when I see them the first time.
\item Line 21 to 24 gives an example of \texttt{scope} . In the environment, all
the lines are drawn in the \texttt{very thick} style.
\item Line 26 to 29 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
when you want to draw a list of objects. In \hyperref[a-minimum-working-example]{the minimum working example} , I
draw a list of short red sticks along with the x-axis and y-axis.
\item Line 31 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
some options between \texttt{[]} and then some text between \texttt{\{\}}. Every node has flexible
anchor options to decide where the text should be placed.
\end{enumerate}
\subsubsection{Another Example}
\label{sec:orgbc1168b}

@@

\subsubsection{Some Basic Rules in TikZ}
\label{sec:orgdb48b38}

@@

\subsubsection{Some tips for in TikZ}
\label{sec:org8e92c4c}

@@

\lstset{language=C,label= ,caption= ,captionpos=b,numbers=none}
\begin{lstlisting}
int main()
{
  int i=0;
  printf();
}
\end{lstlisting}

@@

\section{Projects}
\label{sec:org92a94e0}

\subsection{my workflow of creating a video}
\label{sec:orga6b7968}
\hspace{0pt}\\

@@

\subsubsection{Emacs}
\label{sec:org9c05b58}

@@

\begin{enumerate}
\item program and debug
\label{sec:orge66ddd0}

@@

\item Org mode - journalize your work
\label{sec:org108dfd7}

@@

\item Org mode - get things done
\label{sec:orgb5f62bc}

\item Org mode - write a diary
\label{sec:org168bbcf}

\item Org mode - export your Org file
\label{sec:orgce77f24}

\item program and debug
\label{sec:org6b73797}

\item writing latex
\label{sec:orgf96355a}
\item org-journal
\label{sec:orgc17cd60}

@@

\item ox-hugo
\label{sec:org9e07d00}

@@

\item preview tikz picture in Org
\label{sec:orgab2630d}

@@

\subsubsection{Hugo}
\label{sec:org3f30c08}

@@

I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
about how to leverage Hugo. Ox-hugo helps me do most of the work.
\subsubsection{Hugo Academic Theme}
\label{sec:orgad8a7d5}

@@

\subsubsection{manim}
\label{sec:org022fb8d}

\subsubsection{blender}
\label{sec:org7659274}

\section{Courses}
\label{sec:org85ca59f}
\end{document}

>>>>

\section{Videos}
\label{sec:org1f1f886}

\section{Posts}
\label{sec:org33c9a58}

\subsection{Set up the TikZ in Emacs Org}
\label{sec:org9a1a1dd}
\hspace{0pt}\\

@@

\subsubsection{config the header args}
\label{sec:orgf59efeb}

@@

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\subsubsection{generate results with different formats}
\label{sec:orgebb7e4e}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\subsubsection{export the results according to the backend}
\label{sec:org3858655}

@@

\subsubsection{the final workflow}
\label{sec:org2af511e}

@@

\subsection{Export Markdown and latex using Emacs Org}
\label{sec:orgf87a4ad}

@@

\subsubsection{Introduction}
\label{sec:orgb9aacc7}

@@

\subsubsection{set up ox-hugo}
\label{sec:org0a52bcd}

@@

The first time you want to export an Org file or a subtree of an Org file, use
\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
\subsubsection{use Org Macro replacement}
\label{sec:orgaa4e7a2}

@@

Once you are familiar with Org Macro, It behaves beyond your imagination.
\subsubsection{use the setupfile for each Org file}
\label{sec:orgd15a7e2}

@@

\subsection{Drawing Graphs Using TikZ in Emacs Org}
\label{sec:org5bc49d6}

\subsubsection{Drawing a TikZ picture in Emacs Org Mode}
\label{sec:org8506b3a}

\lstset{language=[LaTeX]TeX,label=a-minimum-working-example,caption={a minimum working example},captionpos=b,firstnumber=1,numbers=left}
\begin{lstlisting}
\usetikzlibrary{intersections,arrows.meta}
\begin{tikzpicture}[thin]
\draw (-1.5,0) -- (1.5,0);
\draw (0,-1.5) -- (0,1.5);
\filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
\draw (0,0) rectangle (.5,.5);
\draw (0,0) rectangle (-0.5,-0.5);
% relative coordinate
\draw[blue, very thick] (30:1) ++ (0,-0.5) --(0,0);
% name a path without drawing it
\path[name path = upward line] (1,0) -- (1,1);
\path[name path = sloped line] (0,0) -- (30:1.5cm);
% use intersection of two path
\draw[name intersections={of = upward line and sloped line, by=x}]
     [very thick, orange] (1,0) -- (x);
% use arrow
\draw[<->>] (0,0) -- (145:1);
\draw[<-{Triangle[fill=red]}] (0,0) -- (30:1);
% use scope
\begin{scope}[very thick]
\draw (-0.4,0.4) -- (0.4,0.4);
\draw (-0.4,-0.4) -- (0.4,-0.4);
\end{scope}
% use foreach
\foreach \x in {-1cm,-0.5cm,1cm}
    \draw[red] (\x,-3pt) -- (\x,3pt);
\foreach \y in {-1cm,-0.5cm,1cm}
    \draw[red](-3pt,\y) -- (3pt,\y);
% using node
\draw (0,0)+(0.2,-0.2) node {\tiny $(0,0)$ };
\end{tikzpicture}
\end{lstlisting}

@@

\begin{enumerate}
\item In \hyperref[a-minimum-working-example]{the minimum working example} line 12 , a path is named  without drawing
it.
\item Line 16 gives an example of using library \texttt{intersections}. Note
that you need to add the library using \texttt{\textbackslash{}usetikzlibrary\{intersections\}}
otherwise an error occurs during \LaTeX compiling.
\item Line 18 and 19 gives an example of using arrow. To make it work,
\texttt{\textbackslash{}usetikzlibrary\{arrows.meta\}} is needed. The library \texttt{arrows.meta} provides tons
of types of arrows whick shock me when I see them the first time.
\item Line 21 to 24 gives an example of \texttt{scope} . In the environment, all
the lines are drawn in the \texttt{very thick} style.
\item Line 26 to 29 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
when you want to draw a list of objects. In \hyperref[a-minimum-working-example]{the minimum working example} , I
draw a list of short red sticks along with the x-axis and y-axis.
\item Line 31 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
some options between \texttt{[]} and then some text between \texttt{\{\}}. Every node has flexible
anchor options to decide where the text should be placed.
\end{enumerate}
\subsubsection{Another Example}
\label{sec:org85bdcaf}

@@

\subsubsection{Some Basic Rules in TikZ}
\label{sec:orge995912}

@@

\subsubsection{Some tips for in TikZ}
\label{sec:org742f086}

@@

\lstset{language=C,label= ,caption= ,captionpos=b,firstnumber=1,numbers=left}
\begin{lstlisting}
int main()
{
  int i=0;
  printf();
}
\end{lstlisting}

@@

\subsection{Walk Through the Petri-Net In TiKZ Tutorial}
\label{sec:orgfaa8657}

\bigin{titlepage}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip}          \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way. If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par
 \end{center}
\endgroup
\end{titlepage}
\newpage

Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
me work through the code line by line. During this example, more tikz libraries
are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
\texttt{tikzpicture} environment.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
\end{center}

\section{Projects}
\label{sec:orgaf97de2}

\subsection{my workflow of creating a video}
\label{sec:org45aac98}
\hspace{0pt}\\

@@

\subsubsection{Emacs}
\label{sec:orgcb16fe3}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgbe5b8cf}

@@

\item Org mode - journalize your work
\label{sec:org5077380}

@@

\item Org mode - get things done
\label{sec:org0286871}

\item Org mode - write a diary
\label{sec:org2d64073}

\item Org mode - export your Org file
\label{sec:orgbd13d0c}

\item program and debug
\label{sec:org53b4991}

\item writing latex
\label{sec:orgce5ad4a}
\item org-journal
\label{sec:orgb58b60d}

@@

\item ox-hugo
\label{sec:org7fc8972}

@@

\item preview tikz picture in Org
\label{sec:org697542b}

@@

\subsubsection{Hugo}
\label{sec:org7cb7cf9}

@@

I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
about how to leverage Hugo. Ox-hugo helps me do most of the work.
\subsubsection{Hugo Academic Theme}
\label{sec:org8323bc3}

@@

\subsubsection{manim}
\label{sec:org00574e3}

\subsubsection{blender}
\label{sec:orgbef2b43}

\section{Courses}
\label{sec:orgeb1cbcd}
